droptlet

### 2021-08-17 analysis/combined.Rmd
as

```{r message = FALSE}
# Packages
options(scipen = 999)
library(rstanarm)
library(brms)
library(scales)
library(tidyverse)
library(emmeans)
library(ggthemes)
library(ggpmisc)
library(cowplot)
library(patchwork)
library(multcomp)
library(ggtext)
library(ggeffects)
library(agricolae)
library(extrafont)
library(showtext)
showtext_auto()
font_add_google("Lato", ## name of Google font
                "lato")  ## name that will be used in R
font_add_google("Roboto", "roboto")

```

@@

model1 <- lmer(deposition ~  trt +
                (1|block/location), 
              data = inswath)
```

```{r eval=FALSE}
isSingular(model1)
```

@@

```{r}
em %>% as_tibble() %>% 
  left_join(inswath) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer)) +
  geom_point(size = 3) +
  geom_jitter(data = inswath %>% 
                rename(emmean = deposition), alpha = 0.1) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  ylim(0, 1550) +
  theme_few() +
  labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none") -> figA
figA +
  ggsave("Figure 1.png", width = 5, height = 5)
```

@@

```{r eval = FALSE}
em2 %>% as_tibble() %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt)) +
  geom_point(size = 3) +
  geom_jitter(data = upwind %>% 
                rename(emmean = deposition), alpha = 0.05) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
#  ylim(0, 0.5) +
  theme_few() +
  labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none") -> figB
figB +
  ggsave("Figure 1B.png", width = 10, height = 5)
```

@@

```{r include=TRUE}
c <- distance_final1 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = fct_reorder(trt, distance_m), 
             y = distance_m,
             label = distance_m, color = trt, shape = hood)) +
  geom_point(size = 3, stroke = 1) +
  scale_shape_manual(values = c(16, 1)) +
  geom_segment(aes(x= trt, xend= trt, y=0, yend=distance_m), size = 2) +
  coord_flip() +
  scale_color_viridis_d(option = "H") + 
  labs(y = "Predicted distance (m)", x = NULL) +
  ylim(0,60) +
  theme_few() +
  theme(legend.position = "none")  
c
```

@@

```{r include=TRUE}
figs <- fig2 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = distance_m, y = predicted, color = trt, 
             fill = trt, label = formula, shape = hood)) +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  geom_line(fill = NA) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
              alpha = 0.3, color = NA) +
  facet_wrap(~ trt, ncol = 3) +
  scale_shape_manual(values = c(16, 1)) + 
  theme_few() +
  geom_label(aes(label = formula), x = 30, y = 20, color = "white") +
  labs(x = "Distance (m)", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_textbox(
          size = 12,
          color = "white", 
          fill = "#494949", 
          box.color = "#282728",
          halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
          padding = margin(2, 0, 1, 0), 
          margin = margin(3, 3, 3, 3))) +
  ggsave("Figure 2.png", width = 6, height = 9)
figs
```

@@

```{r}
epred3$emmeans %>% as_tibble() %>% 
  left_join(auc_data1) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer)) +
  geom_point(size = 3) +
  geom_jitter(data = auc_data %>% 
                rename(emmean = auc), alpha = 0.02) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_few() +
  labs(x = NULL, y = "Area under the curve") +
  theme(legend.position = "none") -> figE
figE
```

@@

```{r}
c + figE + plot_annotation(tag_levels = 'A') -> figU

ggsave("Figure 3.png", width = 10, height = 5)
```

>>>>

```{r message = FALSE}
# Packages
options(scipen = 999)
library(rstanarm)
library(brms)
library(scales)
library(tidyverse)
library(emmeans)
library(ggthemes)
library(ggpmisc)
library(patchwork)
library(ggtext)
library(ggeffects)
library(agricolae)
library(extrafont)
library(showtext)
showtext_auto()
font_add_google("Lato", ## name of Google font
                "lato")  ## name that will be used in R
#font_add_google("Roboto", "roboto")
```

@@

#model1 <- lmer(deposition ~  trt +
#                (1|block/location), 
#              data = inswath)
```

```{r eval=FALSE}
#isSingular(model1)
```

@@

```{r}
library(ggrepel)
em %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = inswath %>% 
                rename(emmean = deposition), alpha = 0.1) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  geom_text_repel(  size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  ylim(0, 2000) +
  theme_few(base_family = "lato") +
  labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        axis.title = element_text(size = 30),
        axis.text = element_text(size = 25)) -> figA

  ggsave("Figure 1.png", width = 5, height = 4)
```

@@

```{r eval = FALSE}
em2 %>% as_tibble() %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt)) +
  geom_point(size = 3) +
  geom_jitter(data = upwind %>% 
                rename(emmean = deposition), alpha = 0.05) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
#  ylim(0, 0.5) +
  theme_few() +
  labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none") -> figB

#  ggsave("Figure 1B.png", width = 10, height = 5)
```

@@

```{r include=TRUE}
c <- distance_final1 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(distance_m = round(distance_m, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, distance_m), 
             y = distance_m,
             label = distance_m, color = trt, shape = hood)) +
  geom_point(size = 3, stroke = 1) +
  geom_text_repel(
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 545) +
  scale_shape_manual(values = c(16, 1)) +
  geom_segment(aes(x= trt, xend= trt, y=0, yend=distance_m), size = 2) +
  coord_flip() +
  scale_color_viridis_d(option = "H") + 
  labs(y = "Predicted distance (m)", x = NULL) +
  ylim(0,60) +
  theme_few(base_family = "lato") +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) 
c
```

@@

```{r include=TRUE}
figs <- fig2 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = distance_m, y = predicted, color = trt, 
             fill = trt, label = formula, shape = hood)) +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  geom_line(fill = NA) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
              alpha = 0.3, color = NA) +
  facet_wrap(~ trt, ncol = 3) +
  scale_shape_manual(values = c(16, 1)) + 
  theme_few(base_family = "lato") +
  geom_label(aes(label = formula), x = 30, y = 20, color = "white", size = 10) +
  labs(x = "Distance (m)", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25),
        strip.background = element_blank(),
        strip.text = element_textbox(
          size = 30,
          color = "white", 
          fill = "#494949", 
          box.color = "#282728",
          halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
          padding = margin(2, 0, 1, 0), 
          margin = margin(3, 3, 3, 3)))

ggsave("Figure 2.png", width = 6, height = 9)
```

@@

```{r}
epred3$emmeans %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = auc_data %>% 
                rename(emmean = auc), alpha = 0.02) +
  scale_color_viridis_d(option = "H") +
  geom_text_repel(
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 545) +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_few(base_family = "lato") +
  labs(x = NULL, y = "Area under the curve") +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> figE
figE
```

@@

```{r}
c + figE +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0)) -> figU

ggsave("Figure 3.png", width = 8, height = 4)
```

### 2021-08-17 analysis/droplet.Rmd
as

```{r}
readxl::read_excel("droplet_data.xlsx")
```

@@

```{r}
fig1 + fig2 + fig3 +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 25, hjust = 0, vjust = 0))

ggsave("Figure 4.png", width = 9, height = 3)
```

>>>>

```{r}
#readxl::read_excel("droplet_data.xlsx")
```

@@

```{r}
fig1 + fig2 + fig3 +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 26, hjust = 0, vjust = 0))

ggsave("Figure 4.png", width = 11, height = 4)
```
